jin_sim

### 2022-11-30 jin_sim.Rmd
Added MC (day of flex) plot.

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
  erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
  fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
  fn_try_deriv <- D(fn_try_deriv,'x')
  x=seq(1,67,length.out=6700)
  tmp <- eval(fn_try_deriv)
  flex_day[i] <- min(x[tmp < 0])
}
flex_day
```

>>>>

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
  erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
  fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
  fn_try_deriv <- D(fn_try_deriv,'x')
  x=seq(1,67,length.out=6700)
  tmp <- eval(fn_try_deriv)
  flex_day[i] <- min(x[tmp < 0])
}
flex_day
```
## MC (day of flex) plot

```{r}
ggplot() +
  geom_point(aes(x=1:m, y=flex_day), color="red")

```
